### 2021-10-13 chapters/introduction.tex
Changes due to examination comments continued

    To aid computation convergence, the BSSNOK method extended the ADM formalism by introducing a conformal factor to the three-metric and selecting a dissipative hyperbolic driver for the  shift vector~\cite{Nakamura1987,Shibata1995,Nakamura1999,Shibata1999,Baumgarte1999,Alcubierre2000,Alcubierre2001}. % Dissipative hyperbolic driver from Alcubierre2001
    The Z4c formalism modified the BSSNOK method by adding a four-vector of constraints, $Z_\mu$, to the Einstein field equations~\cite{Bona2003,Bona2004,Gundlach2005,Bernuzzi2010,Hilditch2013}. 
    This resulted in a propagating Hamiltonian constraint which helps to reduce constraint-violation growth by damping all constraint violations  except for constant modes~\cite{Gundlach2005}.
    Constraint violations can be more easily tracked as non-vanishing values of $Z_\mu$ though particular attention needs to be paid to reflection of constraint violations at boundaries~\cite{Bernuzzi2010,Ruiz2011,Hilditch2013}.  \par

@@

    The aforementioned tools allow the simulation of the late-time merger and post-merger remnant.
    However, there are a number of caveats that need to be considered.
    Firstly, the simulations are expensive, for example, 32 binary neutron star simulations took  $\sim 3\times 10^6\,$CPU hrs to complete~\cite{Takami2015}.
    Because of this, the direct use of numerical-relativity simulations in detection and parameter estimation, where we need large quantities of waveforms, is unfeasible. \par
    Secondly, numerical-relativity simulations unavoidably include numerical viscosity.
    Early simulations show that numerical viscosity could alter the properties of both the neutron star core and the surface~\cite{Shibata2000bar,Cerda-Duran2010}.
    Numerical viscosity was found to introduce phase errors in the late-stage merger and improvements in numerical methods were subsequently introduced to minimise these errors~\cite{Radice2014}.
    The effects of numerical viscosity on the post-merger remnant is less clear, though it was found that numerical viscosity could alter both the neutrino luminosity~\cite{Sekiguchi2016} and the presence of one-armed spiral instability~\cite{Radice2016}.\par

>>>>

    To aid computation convergence, the BSSNOK method extended the ADM formalism by introducing a conformal factor to the three-metric and selecting a dissipative hyperbolic driver for the  shift vector~\cite{Nakamura1987,Shibata1995,Nakamura1999,Shibata1999,Baumgarte1999,Alcubierre2000,Alcubierre2001}. % Dissipative hyperbolic driver from Alcubierre2001
    The Z4c formalism modified the BSSNOK method by adding a four-vector of constraints, $Z_\mu$, to the Einstein field equations~\cite{Bona2003,Bona2004,Gundlach2005,Bernuzzi2010,Hilditch2013}. 
    This resulted in a propagating Hamiltonian constraint which helps to reduce constraint-violation growth by damping all constraint violations  except for constant modes~\cite{Gundlach2005}.
    % Constraint violations can be more easily tracked as non-vanishing values of $Z_\mu$ though particular attention needs to be paid to reflection of constraint violations at boundaries~\cite{Bernuzzi2010,Ruiz2011,Hilditch2013}.  \par
    \redtext{The introduction of $Z_\mu$, given an approapriate gauge, enforces hyperbolic solutions of the Einstein field equations by placing additional constraints on the system, thereby improving convergence~\cite{Bernuzzi2010,Ruiz2011,Hilditch2013}.} \par

@@

    The aforementioned tools allow the simulation of the late-time merger and post-merger remnant.
    However, there are a number of caveats that need to be considered.
    Firstly, the simulations are expensive, for example, 32 binary neutron star simulations took  $\sim 3\times 10^6\,$CPU hrs to complete~\cite{Takami2015}.
    Because of this, the direct use of numerical-relativity simulations in detection and parameter estimation, where we need large quantities of waveforms, is unfeasible. \par
    Secondly, numerical-relativity simulations unavoidably include numerical viscosity.
    \redtext{Early simulations show that numerical viscosity could alter the properties of both the neutron star core and the surface~\cite{Shibata2000bar,Cerda-Duran2010,Bernuzzi2012,Bernuzzi2012b}.}
    Numerical viscosity was found to introduce phase errors in the late-stage merger and improvements in numerical methods were subsequently introduced to minimise these errors~\cite{Radice2014}.
    The effects of numerical viscosity on the post-merger remnant is less clear, though it was found that numerical viscosity could alter both the neutrino luminosity~\cite{Sekiguchi2016} and the presence of one-armed spiral instability~\cite{Radice2016}.\par
